---
title: "Weight of Fish"
author: "Rashonda Weathersby"
date: "April 6, 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

```{r}
Fishdata=read.csv(file="Fish.csv")
```



# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

# Perch

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Perchdata=filter(Fishdata, Species == "Perch")
 Perchdata = subset (Perchdata, select = -Species)
```


## Inferential Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perchdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  

According to the graph height and width is the best. 

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Height+Width,data=Perchdata)
fullup <- lm(Weight~., data=Perchdata)
summary(best.model)
```

The p-value here is so small that this model is an excellent fit. 
```{r}
anova(fullup,best.model)
```
The p-value is 0.879 which means that there is really no difference between using the model that has all of the data vs. the model that uses only 2 variables. 

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->




# Bream

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r}
Breamdata=filter(Fishdata, Species == "Bream")
 Breamdata = subset (Breamdata, select = -Species)
```


## Inferential Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Breamdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  

Length1, Height and Width is the best according to the graph. 

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Length2+Height,data=Breamdata)
fullup <- lm(Weight~., data=Breamdata)
summary(best.model)
```

The p-value here is so small that this model is an excellent fit.

```{r}
anova(fullup,best.model)
```
The p-value is too large to say that there is a difference between the best model which four variables, and the best model that uses two variables. 


<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->




# Smelt

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->


```{r}
Smeltdata=filter(Fishdata, Species == "Smelt")
 Smeltdata = subset (Smeltdata, select = -Species)
```


## Inferential Results

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smeltdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
  
## Which is best??  

The model that is the best, is the one that uses all 4 variables: L1, L2, H, and W. 

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[3,]
```

```{r}
best.model <- lm(Weight~Length2+Width,data =Smeltdata)
fullup <- lm(Weight~., data=Smeltdata)
summary(best.model)
```


```{r}
anova(fullup,best.model)
```
The p-value 0.2521 is to large to say that there is a difference between the best model, that uses four variables, and the best model that uses two variables. 

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Based on the automatic selection of the variables there is no real difference in using a model with two variables versus using one with all of the variables. This was identified through the graphic depiction of the adjusted r squared as well, as the p value. In conclusion, comparing the p value of the two variable models the p value is so small I reject the null hypotheses that these models are beneficial in predicting weight of fish. The p value associated with the anovas, all failed all the hypotheses because they were too large. Meaning there is no differences between the model with two variables versus the full up model. 